Network Structure, Efficiency, and Performance in WikiProjects

### 2018-01-12 paper-content.tex
Update empirical tables and figures.

\begin{table*}[!ht]
\small
\caption{Standardized coefficients for OLS models.
\label{tab:model}
}
\bigskip
\begin{tabular}{lllllllll}
\hline
                               & Perf$_1^\dagger$ & Perf$_2^\dagger$ & A-Eff$_1^\dagger$ & A-Eff$_2^\dagger$ & B-Eff$_1^\dagger$ & B-Eff$_2^\dagger$ & C-Eff$_1^\dagger$ & C-Eff$_2^\dagger$ \\
\hline
Mean degree$^\dagger$          &  -0.84$^{***}$  &  -0.78$^{***}$
                               &  -0.61$^{**}$   &  -0.84$^{***}$
                               &  -0.50$^{***}$  &  -0.61$^{***}$
                               &  -0.34$^{**}$   &  -0.31$^{*}$ \\
In-degree skewness$^\dagger$   &  -0.58$^{***}$  & \+ ---      
                               &  -0.43$^{**}$   & \+ ---      
                               &  -0.19          & \+ ---      
                               &  -0.1           & \+ ---      \\
Out-degree skewness$^\dagger$  &  \+ ---         &  -0.48$^{***}$  
                               &  \+ ---         &  -0.57$^{***}$
                               &  \+ ---         &  -0.26$^{*}$
                               &  \+ ---         &  -0.066 \\
Mean path$^\dagger$            &  -0.357$^{***}$ &  -0.356$^{***}$ 
                               &  -0.026         &  -0.096
                               &  -0.020         &  -0.045
                               &  -0.092$^{**}$  &  -0.086 \\
C-eff$^\dagger$                &  -0.083$^{**}$  & -0.085$^{**}$  
                               &  \+ ---         & \+ ---      
                               &  \+ ---         & \+ ---      
                               &  \+ ---         & \+ --- \\
Connectivity                   & \+0.018         & \+0.016        
                               & \+0.081         & \+0.088
                               & \+0.126$^{***}$ & \+0.142$^{***}$
                               & \+0.080$^{**}$  & \+0.081$^{**}$ \\
Mean editors/article$^\dagger$ & \+0.37$^{***}$  & \+0.40$^{***}$ 
                               & \+0.22          & \+0.27
                               & \+0.20          & \+0.22$^{*}$
                               & \+0.076         & \+0.075 \\
Article count$^\dagger$        &  -0.32          & -0.27          
                               & \+0.63${^*}$    & \+0.70${^*}$ 
                               & \+0.76$^{**}$   & \+0.78$^{**}$
                               & \+0.67$^{***}$  & \+0.67$^{***}$ \\
Editor count$^\dagger$         & \+0.68$^{*}$    & \+0.48         
                               & \+0.74$^{*}$    & \+0.97$^{**}$
                               & \+0.60$^{*}$    & \+0.72$^{**}$
                               & \+0.52$^{*}$    & \+0.46$^{*}$ \\
Revision count$^\dagger$       & \+0.37          & \+0.39         
                               &  -0.84$^{**}$   & -0.88$^{**}$
                               &  -1.05$^{***}$  & -1.05$^{***}$
                               &  -1.00$^{***}$  & -1.00$^{***}$ \\
First assessment               & \+0.028         & \+0.058        
                               & \+0.086$^{*}$   & \+0.101$^{**}$
                               & \+0.309$^{***}$ & \+0.321$^{***}$
                               & \+0.456$^{***}$ & \+0.460$^{***}$ \\
Mean article age               &  -0.040         & -0.029         
                               &  -0.049         & -0.037
                               &  -0.019         & -0.014
                               &  -0.046$^{*}$   & -0.045$^{*}$ \\
\hline
DoF                            & 1278            & 1278          
                               & 1048            & 1048
                               & 1371            & 1371
                               & 1540            & 1540 \\
R$^2_{adj}$                    & 0.37            & 0.37          
                               & 0.15            & 0.16
                               & 0.30            & 0.30
                               & 0.43            & 0.43 \\
\hline
\end{tabular}
\begin{tablenotes}
\item $\dagger$ Log-transformed. * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
\end{tablenotes}
\end{table*}

To study the relationship between network structure, efficiency, and performance,
we model the performance and efficiency of WikiProjects using ordinary least-squares linear regression.
Each WikiProject is taken as a single observation.
The models include each project's coeditor network properties as independent variables.
We also include several project-level variables to control for confounding factors,
described below.
\begin{description}
\item[C-efficiency] Quantifies how quickly a WikiProject improves low-quality articles.
\item[Connected fraction] Fraction of coeditor pairs connected by a path.
\item[Mean editors/article] Mean number of editors collaborating on each article in a WikiProject.
\item[Article count] Total number of articles in the WikiProject.
\item[Editor count] Total number of editors working on articles within a WikiProject.
\item[Revision count] Total number of revisions to articles in a WikiProject.
\item[First assessment] Timesamp of first assessment; a measure of how long a WikiProject has been active.
\item[Mean article age] Mean age of articles within a WikiProject.
\item[Mean similarity] Mean Jaccard similarity (by article) with other WikiProjects; a measure of topical complexity.
\end{description}

@@

Past work in the field of social learning typically models collaboration
as an optimization problem:
finding a state of the world which maximizes some objective function
\cite{lazer_network_2007,mason_propagation_2008,mason_collaborative_2012,barkoczi_social_2016}.
Wikipedia itself can be regarded as an optimization problem.
On Wikipedia, editors are generally seeking to improve the quality of articles
and have some personal preference over possible states of an article.
When editors do not agree on the optimal state of an article,
the conflict is resolved through a consensus-based deliberation.
This consensus process can be regarded as a {\em social choice function}
\cite{arrow_social_2012,brandt_computational_2012}
which maps individual preferences to community preferences.
Wikipedia can thus be thought of as a group of editors with individual preferences
for article states,
collaborating to optimize articles according to community preferences.

@@

In social learning,
agents can also incorporate information from
other agents they are connected to by a network edge.
While individual learning always converges to the local maximum relative to the starting point,
social learning strategies allow agents to ``jump'' to drastically different solutions with higher local maxima.
In our model, we use both the conformity and best-neighbor strategies from \cite{barkoczi_social_2016}.
In the {\em best-neighbor} strategy, each agent compares its solution to a sample of its
neighbors, and chooses the solution with the highest value.
In order to compare solutions between neighbors,
the exact value of the objective function must be known for each solution,
so this strategy does not satisfy the unknown objective assumption
or the limited concern assumption.
In the {\em conformity} strategy, agents simply choose the most common solution among their neighbors
(ties are broken uniformly at random).
This strategy does not rely on solution value at all, so clearly satisfies the
unknown objective assumption,
but it fails to satisfy the limited concern assumption because it updates all
bits of the NK solution.
In both cases, a single iteration of individual learning is performed after each social learning
iteration.
Because each agent maintains a separate estimate of the solution,
neither of these strategies satisfies the single source of truth assumption.

@@

In order to satisfy the single source of truth assumption,
we introduce a new strategy, which we call the local majority strategy.
In {\em local majority}, agents begin with exactly the same starting state,
and apply individual learning to their concern to generate
possible improvements to the solution.
Next, a new solution is constructed by considering each locus of the NK solution
individually.
Every agent concerned with a bit votes for its state based on their preferred
new solution and the majority state is chosen.
The result of this process is that all agents agree on a single improved state,
which forms the basis for the next iteration.
This strategy more realistically reflects collaborations like Wikipedia:
at any given time, a Wikipedia article has a single state, determined by consensus,
but editors may have differing opinions on how to improve that article.

@@

We simulated 100 trials for rewiring values of 0.0, 0.167, 0.333, 0.5, 0.667, 0.833, and 1.0.
For each trial we generated an NK model with N=250 and K=7 and ran each social learning strategy
for 300 iterations,
as well as a network based on that NK model and rewired.
We confirmed that all trials converged to their maximum value before reaching the last iteration.
Some statistics on the network properties of the networks are summarized in Table \ref{tab:stats}.
We see that the coefficient of variation of degree is approximately 10\%,
while only 1\% for mean path length, confirming that the rewiring process has a stronger influence
on degree than on path length.

\begin{table}
\small
\centering
\caption{
Simulated network statistics.
\label{tab:stats}
}
\bigskip
\begin{tabular}{lcc}
\hline
Property          & Mean  & Std. Dev. \\
\hline
Mean Degree       & 132.3 & 9.2 \\
Mean Path length  & 1.735 & 0.019 \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}
\small
\caption{
Efficiency regression coefficients.
\label{tab:sim-eff}
}
\centering
\bigskip
\begin{tabular}{llc}
\hline
Strategy & Std. Coeff. \\
\hline
Best-neighbor       & -0.064 \\
Conformity          & -0.080 \\
Local best-neighbor & -0.086 \\
Local conformity    & \+0.049 \\
Consensus           & -0.0325$^{***}$ \\
\hline
\end{tabular}
\begin{tablenotes}
\item \centering * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
\end{tablenotes}
\end{table}

\begin{table}
\small
\caption{
Performance regression coefficients.
\label{tab:sim-perf}
}
\centering
\bigskip
\begin{tabular}{llc}
\hline
Strategy & Std. Coeff. \\
\hline
Best-neighbor       & \+0.084 \\
Conformity          & \+0.130 \\
Local best-neighbor & -0.080 \\
Local conformity    & -0.020 \\
Consensus           & \+2.38$\times{10^{-4\;**}}$ \\
\hline
\end{tabular}
\begin{tablenotes}
\item \centering * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
\end{tablenotes}
\end{table}

>>>>

\begin{table}
\small
\caption{Standardized coefficients for OLS models.
\label{tab:model}
}
\bigskip
\begin{tabular}{lllllllll}
&Perf$^\dagger$&A-Eff$^\dagger$&B-Eff$^\dagger$&C-Eff$^\dagger$\\
\hline
Mean degree$^\dagger$&-0.7$^{***}$&-0.8$^{***}$&-0.6$^{***}$&-0.3$^{*}$\\
Out degree skew$^\dagger$&-0.4$^{***}$&-0.5$^{**}$&-0.3$^{*}$&-0.06\\
Mean path length$^\dagger$&-0.33$^{***}$&-0.09&-0.05&-0.09\\
C-Efficiency$^\dagger$&-0.08$^{*}$&\+---&\+---&\+---\\
Connected frac.&0.01&0.09$^{*}$&0.15$^{***}$&0.06\\
Talk fraction$^\dagger$&0&-0.02&-0.03&0.01\\
Mean similarity$^\dagger$&0.06$^{**}$&-0.03&0.01&0.02\\
Mean editors/art.$^\dagger$&0.3$^{**}$&0.3&0.2$^{*}$&0.09\\
Article count$^\dagger$&-0.4&0.7$^{*}$&0.8$^{**}$&0.7$^{**}$\\
Editor count$^\dagger$&0.4&0.9$^{**}$&0.8$^{**}$&0.5$^{*}$\\
Revision count$^\dagger$&0.6$^{*}$&-1$^{**}$&-1.1$^{***}$&-1$^{***}$\\
First assessment&0.05&0.11$^{**}$&0.31$^{***}$&0.43$^{***}$\\
Mean article age&-0.03&-0.04&-0.01&-0.05$^{*}$\\
\hline
N&1179&966&1260&1415\\
R$^2_{adj}$&0.37&0.17&0.30&0.43\\
\hline
\end{tabular}
\begin{tablenotes}
\item $\dagger$ Log-transformed. * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
\end{tablenotes}
\end{table}

To study the relationship between network structure, efficiency, and performance,
we model the performance and efficiency of WikiProjects using ordinary least-squares linear regression.
Each WikiProject is taken as a single observation.
The models include each project's coeditor network properties as independent variables.
We also include several project-level variables to control for confounding factors,
described below.
\begin{description}
\item[C-efficiency] Quantifies how quickly a WikiProject improves low-quality articles.
\item[Connected fraction] Fraction of coeditor pairs connected by a path.
\item[Talk fraction] Fraction of total revisions made to talk pages.
\item[Mean editors/article] Mean number of editors collaborating on each article in a WikiProject.
\item[Article count] Total number of articles in the WikiProject.
\item[Editor count] Total number of editors working on articles within a WikiProject.
\item[Revision count] Total number of revisions to articles in a WikiProject.
\item[First assessment] Timesamp of first assessment; a measure of how long a WikiProject has been active.
\item[Mean article age] Mean age of articles within a WikiProject.
\item[Mean similarity] Mean Jaccard similarity (by article) with other WikiProjects; a measure of topical complexity.
\end{description}

@@

Past work in the field of social learning typically models collaboration
as an optimization problem:
finding a state of the world which maximizes some objective function
\cite{lazer_network_2007,mason_propagation_2008,mason_collaborative_2012,barkoczi_social_2016}.
Wikipedia itself can be regarded as an optimization problem.
On Wikipedia, editors are generally seeking to improve the quality of articles
and have some personal preference over possible states of an article.
When editors do not agree on the optimal state of an article,
the conflict is resolved through a consensus-based deliberation.
This consensus process can be regarded as a {\em social choice function}
\cite{arrow_social_2012,brandt_computational_2012}
which maps individual preferences to community preferences.
Wikipedia can thus be thought of as a group of editors with individual preferences
for article states,
collaborating to optimize articles according to community preferences.
Note that these community preferences don't assume the existence of any
ground truth, other than the preferences themselves.

@@

In social learning,
agents can also incorporate information from
other agents they are connected to by a network edge.
While individual learning always converges to the local maximum relative to the starting point,
social learning strategies allow agents to ``jump'' to drastically different solutions with higher local maxima.
In our model, we use both the conformity and best-neighbor strategies from \cite{barkoczi_social_2016}.
In the {\em best-neighbor} strategy, each agent compares its solution to a sample of its
neighbors, and chooses the solution with the highest value.
In order to compare solutions between neighbors,
the exact value of the objective function must be known for each solution,
so this strategy does not satisfy the unknown objective assumption
or the limited concern assumption.
In the {\em conformity} strategy, agents simply choose the most common solution among their neighbors
(ties are broken uniformly at random).
This strategy does not rely on solution value at all, so clearly satisfies the
unknown objective and limited concern assumptions.
In both cases, a single iteration of individual learning is performed after each social learning
iteration.
Because each agent maintains a separate estimate of the solution,
neither of these strategies satisfies the single source of truth assumption.

@@

In order to satisfy the single source of truth assumption,
we introduce a new strategy, which we call the local majority strategy.
In {\em local majority}, agents all begin with the same starting state,
and apply individual learning to their concern to generate
possible improvements to the solution.
Next, a new solution is constructed by considering each locus of the NK solution
individually.
Every agent concerned with a bit votes for its state based on their preferred
new solution and the majority state is chosen.
The result of this process is that all agents agree on a single improved state,
which forms the basis for the next iteration.
This strategy more realistically reflects collaborations like Wikipedia:
at any given time, a Wikipedia article has a single state, determined by consensus,
but editors may have differing opinions on how to improve that article.

\begin{table*}
\small
\centering
\caption{
Social learning strategies
\label{tab:strat}
}
\bigskip
\begin{tabular}{lccccc}
Name          & Social & Individual & Limited concern & Unknown objective & Single truth \\
\hline
Best+I & Best neighbor   & Global & & & \\
Conf+I & Conformity      & Global & & \Checkmark & \\
Best+LI & Best neighbor  & Local  & \Checkmark & & \\
Conf+LI & Conformity     & Local  & \Checkmark & \Checkmark & \\
LMaj+LI & Local majority & Local  & \Checkmark & \Checkmark & \Checkmark \\
\hline
\end{tabular}
\end{table*}

@@

We simulated 100 trials for rewiring values of 0.0, 0.167, 0.333, 0.5, 0.667, 0.833, and 1.0.
For each trial we generated an NK model with N=250 and K=7 and ran each social learning strategy
(Table \ref{tab:strat}) for 300 iterations,
as well as a network based on that NK model and rewired.
For conformity and best-neighbor strategy, we used a sample size of 3, following
\cite{barkoczi_social_2016}.
We confirmed that all trials converged to their maximum value before reaching the last iteration.
Some statistics on the network properties of the networks are summarized in Table \ref{tab:stats}.
We see that the coefficient of variation of degree is approximately 10\%,
while only 1\% for mean path length, confirming that the rewiring process has a stronger influence
on degree than on path length.

\begin{table}
\small
\centering
\caption{
Simulated network statistics.
\label{tab:stats}
}
\bigskip
\begin{tabular}{lcc}
Property          & Mean  & Std. Dev. \\
\hline
Mean Degree       & 132.3 & 9.2 \\
Mean Path length  & 1.735 & 0.019 \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}
\small
\caption{
Efficiency regression coefficients.
\label{tab:sim-eff}
}
\centering
\bigskip
\begin{tabular}{llc}
Strategy & Std. Coeff. \\
\hline
Best-neighbor       & -0.064 \\
Conformity          & -0.080 \\
Local best-neighbor & -0.086 \\
Local conformity    & \+0.049 \\
Consensus           & -0.0325$^{***}$ \\
\hline
\end{tabular}
\begin{tablenotes}
\item \centering * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
\end{tablenotes}
\end{table}

\begin{table}
\small
\caption{
Performance regression coefficients.
\label{tab:sim-perf}
}
\centering
\bigskip
\begin{tabular}{llc}
Strategy & Std. Coeff. \\
\hline
Best-neighbor       & \+0.084 \\
Conformity          & \+0.130 \\
Local best-neighbor & -0.080 \\
Local conformity    & -0.020 \\
Consensus           & \+2.38$\times{10^{-4\;**}}$ \\
\hline
\end{tabular}
\begin{tablenotes}
\item \centering * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
\end{tablenotes}
\end{table}
